TBD

### 2020-11-03 outputs/paper/paper.Rmd
8.12

```{r}
# Setup data for the pie chart and mutate a variable that details proportions for various responses. 
incomeinfo <- tbdata %>% group_by(household_income_grouped) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
# Graph the pie chart using ggplot; Set colour scheme, font, etc. 
incomegraph <- incomeinfo %>% ggplot(aes(x = "", y = prop, fill = household_income_grouped)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Accent") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "", fill="Household Income") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4.7) +
     theme(text = element_text(size=13))
incomegraph
```

@@

```{r}
# Setup data for the pie chart and mutate a variable that details proportions for various responses. 
educationinfo <- tbdata %>% group_by(education_grouped) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
# Graph the pie chart using ggplot; Set colour scheme, font, etc. 
educationgraph <- educationinfo %>% ggplot(aes(x = "", y = prop, fill = education_grouped)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Set2") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "", fill="Education") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4) +
     theme(text = element_text(size=13))
educationgraph
```

```{r}
# Setup data for the pie chart and mutate a variable that details proportions for various responses. 
ageinfo <- tbdata %>% group_by(age_group) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
# Graph the pie chart using ggplot; Set colour scheme, font, etc. 
agegraph <- ageinfo %>% ggplot(aes(x = "", y = prop, fill = age_group)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Set3") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "", fill="Age Groups") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=45, size = 4)+
     theme(text = element_text(size=13))
agegraph
```

>>>>

```{r}
# Setup data for the pie chart and mutate a variable that details proportions for various responses. 
incomeinfo <- tbdata %>% group_by(household_income_grouped) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
# Graph the pie chart using ggplot; Set colour scheme, font, etc. 
incomegraph <- incomeinfo %>% ggplot(aes(x = "", y = prop, fill = household_income_grouped)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Accent") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "", fill="Household Income") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=0, size = 4.7) +
     theme(text = element_text(size=13))
incomegraph
```

@@

```{r}
# Setup data for the pie chart and mutate a variable that details proportions for various responses. 
educationinfo <- tbdata %>% group_by(education_grouped) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
# Graph the pie chart using ggplot; Set colour scheme, font, etc. 
educationgraph <- educationinfo %>% ggplot(aes(x = "", y = prop, fill = education_grouped)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Set2") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "", fill="Education") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=0, size = 4) +
     theme(text = element_text(size=13))
educationgraph
```

```{r}
# Setup data for the pie chart and mutate a variable that details proportions for various responses. 
ageinfo <- tbdata %>% group_by(age_group) %>% summarise(n=n()) %>% mutate(prop = 100*(n/sum(n)))
# Graph the pie chart using ggplot; Set colour scheme, font, etc. 
agegraph <- ageinfo %>% ggplot(aes(x = "", y = prop, fill = age_group)) + 
      geom_bar(width = 1, stat = "identity") + 
      coord_polar("y", start = 0) +
      scale_fill_brewer(palette = "Set3") +
      theme_void() +
      ylab("") + xlab("") + 
     labs(title = "", fill="Age Groups") +
     geom_text(aes(label = paste0(round(prop), "%")), position = position_stack(vjust = 0.5), angle=0, size = 4)+
     theme(text = element_text(size=13))
agegraph
```
